Visual inference for networks

### 2016-02-22 paper/network-inference.Rnw
add model description

\par One network model we examine is the stochastic actor-oriented models introduced by Snijders~\cite{Snijders:1996}. Social networks are generally not static: they evolve over time and this evolution is influenced by the actors and the network structure. Estimation and implementation of these models can be done in the RSIENA software~\cite{RSiena}.  The software allows many possible effects to be included in this type of model, given below. XX insert math after I read the Snijders papers XX  Some of the network effects and actor effects we look at are XXX insert list of effects XXX.

>>>>

\par One network model we examine is the stochastic actor-oriented models (SAOM) introduced by Snijders~\cite{Snijders:1996}. Social networks are generally not static: they evolve over time and this evolution is influenced by the actors and the network structure. In SAOMs, each node, or actor, has its own objective function, $f_i(\beta, x)$ where $i$ is the node index, and $\beta$ is a vector of $p$ coefficients for the $p$ effects in a model, $s_{ki}(x)$ for a given network state $x$, effect $k = 1, ..., p$ and node $i$. The values of each $\beta_k$ are estimated with all nodes and ties in consideration and are applied to all nodes' objective functions.
\par At random moments (occurring with rate $\rho$), a single actor $i$ is permitted to change one of its ties, $x_{ij}$. Or, the actor can do nothing. These single edge change moments are unobserved. They are only observed in aggregate when the network is observed at discrete time points. 
\par When given the opportunity to change or not, each actor tries to optimize its own objective function $f_i(\beta,x)$ under the current configuration of the network (denoted by $x$) in the observed time point.  The probability that node $i$ will change a tie $x_ij$ when given the opportunity to act is $$ p_{ij} = \frac{\exp(f(\beta,x| x_{ij}=x'_{ij}) - f(\beta, x |x_{ij}=x_{ij}))}{\sum_{h=1}^n \exp(f(\beta, x |x_{ih}=x'_{ih}) - f(\beta, x|x_{ih}=x_{ih}))}$$

where $x'_{ij}$ is the opposite of the current state of $x_{ij}$.

\par Estimation and implementation of these models can be done in the RSIENA software~\cite{RSiena}.  The software allows many possible effects to be included in this type of model, given below. XX insert math after I read the Snijders papers XX  Some of the network effects and actor effects we look at are XXX insert list of effects XXX.
